Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-16 paper/main.tex
Dissolve acronymns

\noindent Generally

\begin{itemize}
    \item imo AD and AV can be written as movie and audio-description
\end{itemize}

@@

% open question
In this study, we investigate if increased hemodynamic activity in the PPA that
is usually revealed by contrasting blocks of pictures can also be revealed under
more ecologically conditions.
% we use 2 naturalistic stimuli
To answer this question, we operationalized the perception of both visual and
auditory spatial information using two naturalistic stimuli (see
\citep{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic} for reviews).
% AV stimulus
The operationalization of visual perception is based on an annotation of cuts
and depicted locations in the audio-visual movie ``Forrest Gump'' (AV stimulus).
% AO stimulus
The operationalization of auditory perception is based on an annotation of
speech occurring in the movie's audio-description (AD stimulus).
% GLM contrasts
We then created several general linear model (GLM) contrasts to analyze the
corresponding publicly available fMRI datasets of each naturalistic stimulus
\citep{hanke2016simultaneous, hanke2014audiomovie}
(\href{http://www.studyforrest.org}{studyforrest.org}).

@@

\subsection{Participants}
% AD study
In the AD study \citep{hanke2014audiomovie}, 20 German native speakers (all
right-handed, age 21–38 years, mean age 26.6 years, 12 male) listened to the
German audio-description \citep{ForrestGumpGermanAD} of the movie ``Forrest
Gump'' \citep{ForrestGumpMovie}.
% AV study
In the AV study \citep{hanke2016simultaneous}, 15 participants (21–39 years,
mean age 29.4, six female) of the prior AD study watched the audio-visual movie
with dubbed German audio track \citep{ForrestGumpDVD}.
% VIS study
In the VIS study \citep{sengupta2016extension}, the same 15 participants took
part in a six-category block-design visual localizer.

@@

% AD
In the AD study, visual instructions were presented on a rear-projection screen
inside scanner bore. During the
functional scans, the projector presented a medium gray screen with the primary
purpose to illuminate a participant's visual field in order to prevent premature
fatigue.
% AV & VIS
In the AV and VIS study, visual instructions and stimuli were presented on a
rear-projection screen
% screen size \unit[23.75 $\times$ 10.25]{cm}
at a viewing distance of \unit[63]{cm}, with a movie frame projection size
approximately \unit[21.3]$^{\circ}$ $\times$ \unit[9.3]$^{\circ}$.
% angle of view: VIS
In the VIS study, stimulus images were displayed at a size of approximately
\unit[10]$^{\circ}$ $\times$ \unit[10]$^{\circ}$ of visual angle.
% AD & AV: auditory stimulation
Auditory stimulation was implemented using custom in-ear (AD), or over-the-ear
headphones (AV), which reduced the scanner noise by
at least \unit[20–30]{dB}.

@@

Gradient-echo fMRI data for the AD study were acquired using a \unit[7]{Tesla}
Siemens MAGNETOM magnetic resonance scanner equipped with a 32 channel brain
receive coil at \unit[2]{s} repetition time (TR) with 36 axial slices (thickness
\unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane resolution, \unit[224]{mm}
field-of-view, anterior-to-posterior phase encoding direction) and a
\unit[10]{\%} inter-slice gap, recorded in ascending order.
% slice orientation
Slices were oriented to include the ventral portions of frontal and occipital
cortex while minimizing intersection with the eyeballs.
% FOV
The field of view was centered on the approximate location of Heschl's gyrus.
% motion correction
EPI images were online-corrected for motion and geometric distortions.

% AV & VIS
In the AV and VIS study, a \unit[3]{Tesla} Philips Achieva dStream
MRI scanner with a 32 channel head coil acquired gradient-echo fMRI data
at \unit[2]{s} repetition time with
% slices
35 axial slices (thickness \unit[3.0]{mm}, \unit[10]{\%} inter-slice gap) with
\unit[80 $\times$ 80]{voxels} (\unit[3.0 $\times$ 3.0]{mm} of in-plane
resolution, \unit[240]{mm} field-of-view) and an anterior-to-posterior phase
encoding direction, recorded in ascending order.
% no. of volumes
A total of 3599 volumes were recorded for each participant in each of the
naturalistic stimulus paradigms (AD and AV).

@@

% data sources
% https://github.com/psychoinformatics-de/studyforrest-data-aligned/tree/master/code
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}
All analyses presented here are based on previously published fMRI data
(\url{https://github.com/psychoinformatics-de/studyforrest-data-aligned}).
Of those 15 participants in the studyforrest dataset that took
part in all three experiments,
% exclusion of VP 10
data of one participant were dropped to due to invalid distortion correction
during scanning of the AD stimulus.
Data were previously corrected for motion, aligned with and re-sliced onto a
participant-specific BOLD template image \citep{sengupta2016extension}
(uniform spatial resolution of \unit[2.5$\times$2.5$\times$2.5]{mm} for both
AD and AV data).
% preprocessing intro
All analyses presented here were carried out using
FSL v5.0.9 (\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software Library};
\citep{smith2004fsl}) on a computer cluster running the Debian GNU/Linux
operating system. Software packages were obtained from repositories of
\href{http://neuro.debian.net}{NeuroDebian} \citep{halchenko2012open}.

@@

% AV anno
For the analysis of the AV stimulus, we took advantage of a previously published
annotation of 869 movie cuts and the depicted location after each cut
\citep{haeusler2016cutanno}.
% rationale to use that annotation rationale behind using movie cuts
Our rationale was that cuts are ``spatially relevant'' events that re-orient the
viewer within the environment of the movie by either switching to another
setting or switching the perspective within the same setting.
% AV regressors/events
Each cut was put into one of the following five categories (see Table
\ref{tab:av-events}):
%
1) a cut switching to a setting that was depicted for the first time
(\texttt{vse\_new}),
%
2) a cut switching to a setting that was already depicted earlier in the movie
(\texttt{vse\_old}),
%
3) a cut switching to another locale within a setting (\texttt{vlo\_ch}; e.g. a
cut from first to the second floor in Forrest's house),
%
4) a cut to another camera position within a setting or locale that was depicted
for the first time (\texttt{vpe\_new}), and
%
5) a cut to another camera position within a setting or locale that was already
depicted before (\texttt{vpe\_old}).

@@

% AD annotation
For the analysis of the AD stimulus, we extended a publicly available annotation
of speech \citep{hausler2021studyforrest} by further annotating words spoken by
the audio-description's narrator.
% annotation procedure
Two persons performed a categorization of (concrete and countable) nouns that
the narrator uses to describe the movie's missing visual content based on a set
of rules.
% preliminary annotation
A preliminary annotation was performed by one person according to the rules.
% corrections
Minor corrections due to incorrectly applied rules were done by the author.
% reference to table with rules and examples
A complete overview of all 18 noun categories, the rule for a word to belong to
a category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% why and how of categories 1
Some categories reflect the verbal counterpart of the stimulus categories that
were used in the visual localizer experiment (e.g. \texttt{body}, \texttt{face},
\texttt{head}, \texttt{object}, \texttt{setting\_new}, and
\texttt{setting\_rec}).
% why and how of categories 2
Other categories were created to semantically cluster remaining nouns into
categories that had no counterpart in the visual localizer experiment (e.g.
\texttt{bodypart}, \texttt{female}, \texttt{fname}, \texttt{furniture},
\texttt{geo}, \texttt{geo-room}, \texttt{male}, and \texttt{persons}).
% categories in detail
%Nouns were categorized by the verbal clue they provide about the
%cinematographic scene's environment (\texttt{geo}, \texttt{geo-room};
%\texttt{setting\_new}, \texttt{setting\_old}), its inherent persons (e.g.
%\texttt{female}, \texttt{male}, \texttt{persons}), a person's body or worn
%clothes (\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a
%scene's inherent objects (\texttt{object}, \texttt{furniture}).  problem with
%hierarchical categories
The categories \texttt{setting\_new} and \texttt{setting\_rec} comprise not just
words that describe a setting as a whole (e.g. ``[in] Greenbow'', ``[in a]
disco'', ``[the platoon wades through a] rice field''). They also comprise words
that could count as a member of another category in case the narrator uses
these words to indicate a switch from one setting to another (e.g. ``[a]
physician'').
% how it was handled
These nouns were flagged with both categories during the initial annotation
procedure. In context of the current analyses these word are considered to
belong exclusively to the higher-level category of changing a setting
(\texttt{se\_new} or \texttt{se\_old}).
% pooling of categories
Some noun categories that were semantically similar and offered only a small
amount of counts were pooled resulting in 11 final event categories (see Table
\ref{tab:ao-events}). These event categories were then used to model hemodynamic
responses.

@@

% low-leve confounds: intro
Lastly, we algorithmically annotated the temporal structure of low-level
perceptual features to create nuisance regressors.
% visual shit
For the AV stimulus, we computed the mean luminance of a movie frame
(\unit[40]{ms}), the difference in mean luminance of each frame's left and right
half, the difference in mean luminance of the lower and upper half, and finally
the perceptual difference of consecutive frames.
% auditory shit
Finally for both audio tracks, we computed the left-right difference in volume
and root mean square energy averaged across the length of every movie frame
(\unit[40]{ms}).

@@

% movie events
The events of the movie cut related categories and \texttt{no\_cut} events were
modeled as box car events of 200 ms duration.
%
Nouns were modeled from onset to offset of each word, low-level confounds from
onset to offset of the corresponding movie frame
% convolving
Events for all regressors of the AV and AO stimulus were convolved with a double
gamma hemodynamic response function (HRF).

@@

% AV design matrix
For the subsequent first level GLM analysis of the AV stimulus, the modeled
hemodynamic responses related to all movie cuts (including \texttt{no\_cut}) and
six low-level perceptual confounds were included as regressors in the design
matrix.
% AD regressors in AV AD design matrix
For the first level analysis of the AD stimulus, the modeled hemodynamic
responses related to all noun categories and the two low-level perceptual
confounds were included.
% AD regressors in AV
To create a contrasts of cross-modal control in the analysis of the AV stimulus,
we also implemented the regressors based on nouns used by the
audio-description's narrator to indicate a switch to another setting (categories
\texttt{se\_new} and \texttt{se\_old}).
% AV regressors in AV
To create contrasts of cross-modal negative control in the analysis of the AD
stimulus, we also implemented the movie cut-related regressors
(excluding \texttt{no\_cut}).
% both stimuli: null regressors
For both stimuli, a null regressor was chosen for a event category in a segment,
if that segment did not contain an event of the category (e.g. no event of
\texttt{vpe\_old} in segment 3; cf. Table \ref{tab:ao-events}).
% temporal derivatives
Temporal derivatives were included in the design matrix to compensate for
regional differences between modeled and actual HRF \citep{friston1998event}.
% motion parameters
Six motion parameters were also included.
% high-pass filtering
Finally, designs were filtered with the same high-pass filter (cutoff period of
\unit[150]{s}) as the BOLD time series.

@@

% similar to previous studies
On the first level, we created GLM contrasts based on annotated stimulus
features embedded in the in the audio-visual movie and its audio-description.
% intro
To test the robustness of this approach, we operationalized the perception of
spatial information compared to the perception of non-spatial information
differently in five $t$-contrasts for the AV stimulus (see Table
\ref{tab:av-contrasts}) and eight $t$-contrasts for the AD stimulus (see Table
\ref{tab:ao-contrasts}).
% reason: robustness
We assumed all contrasts could in principle correlate with increased hemodynamic
activity in the PPA but chose one contrast to be the ``primary contrast'' for
later detailed inspection and report.
% selection criteria for primary contrast.
The selection criterion for the primary contrast of each stimulus was a
subjectively good balance between a) how well the average of events within
categories represented spatial information and non-spatial information
respectively (cf. section \ref{rationale}), and b) the amount of available data.
% AV: primary contrast
In the primary contrast of the AV stimulus, we contrasted cuts to a setting that
was not depicted before (\texttt{vse\_new}) to cuts merely switching the camera
position within a setting that was already established earlier in the movie
(\texttt{vpe\_old}).
% why
We assumed that the category \texttt{vse\_new} on average comprised the most
movie frames depicting a landscape or the geometry of a setting, and the
category \texttt{vpe\_old} the most frames depicting persons, faces, or objects
[(cf.  rationale to categorize the cuts in section \ref{rationale})].
% AD: primary contrast
In the primary contrast of the AD stimulus, we contrasted buildings and
landmarks (\texttt{geo}), and rooms and geometry-defining objects
(\texttt{geo-room}) with not just nouns referring to a person's head or face
(\texttt{fahead}, N=83; e.g.  ``eyes'', ``face'', or ``head'') but also all
non-geometry related categories (\texttt{body}, \texttt{bodypart},
\texttt{fahead}, \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}) except
\texttt{furniture} to get more events per stimulus segment.\todo{ouff}
% why furniture was not used
The category ``furniture'' (\texttt{furn}) was not used as a regressor of
interest in any contrast because these nouns could be perceived as either a
geometry-defining scene element or as an isolated object.
% why se_new & se_old were not used in the primary contrasts
The categories of nouns indicating a switch to a setting that occurred for the
first time (\texttt{se\_new}) or a setting that recurred during the plot
(\texttt{se\_old}) were not included in the primary contrast because
% heterogeneous category
a) categories comprise nouns that could count as a member of another category
(e.g. ``[a] physician''; section \ref{rationale}), and
% richness of verbal description vs. picture
b) nouns that only vaguely describe a scene (e.g. ``[in] Greenbow'', ``[in a]
disco'', ''[black and white] film recordings'') [compared to whole, perceptually
richer pictures].
% and c) the narrator is often lacking behind a short dialogue or a change of
% the soundscape that might already indicate a change of settings.

% control contrasts
Finally, we created several $t$-contrasts as negative controls for both stimuli
(see Tables \ref{tab:av-contrasts} and \ref{tab:ao-contrasts}).
% AV: no cut > cut
For the AV stimulus, four contrasts were created contrasting the no-cut
regressor (\texttt{vno\_cut} to cut-related regressors \ref{tab:av-contrasts}).
% AV: narrator
One contrast (\texttt{vs\_new} > \texttt{vpe\_old}) was created by contrasting
nouns spoken by the narrator.
% AD stimulus
For the AD stimulus, we created five $t$-contrasts (see Table
\ref{tab:ao-contrasts}) to test if increased activation in the PPA was
correlated with moments of cuts.

@@

% one contrast to localize them all; "...and Z>3.4 for all"
Contrary to \citep{sengupta2016extension}, we here used the same contrast of
each naturalistic stimulus and the same threshold for all subjects.
% subject space -> NeuroVault
Results of the analyses that were performed in subject-space can be found in the
accompanying dataset (Z>2.3, p<.05 cluster-corrected).
% here report in group space
For better comparisons of subjects, we here report results from the analyses
performed in group space (Z>3.4, p<.05 cluster-corrected).
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AV
and AD $t$-contrast, and the outline of overlapped, individual PPAs
co-registered to the MNI152 template.
% one slice to show them all
Transversal slice of z=-11 was chosen as it depicts voxels of
significant clusters in almost all subjects.

% AV
Results of the primary AV contrast yielded bilateral clusters in five subjects,
a unilateral right cluster in six subjects (of which one subjects yielded a
unilateral cluster in the visual localizer), and a unilateral left cluster in
one subject.
% difference to dedicated localizer
We find homologous clusters in sub-20, whereas the dedicated visual localizer
yielded only one cluster in the right hemisphere.

% report here in group
Results of the primary AD contrast yielded bilateral clusters in nine subjects
that are within or overlapping with the individual PPA.
% subj-04
In sub-04, two homologous clusters are apparent, whereas the dedicated localizer
(and AV stimulus) yielded only one cluster in the right hemisphere.
% sub-09
In sub-09 the analysis yielded one cluster in the left-hemispheric PPA.

\begin{figure*}[h!]
\centering
    \includegraphics[width=\linewidth]{figures/subs-thresh-ppa}
    \caption{Fixed-effects individual-level GLM results (Z>3.4, p<.05
        cluster-corrected).
        Individual brains are aligned via non-linear
        transformation to a study-specific T2* group template that is
        co-registered to the MNI152 template with an affine transformation (12
        degrees of freedom).
        The results of the audio-description's primary
        $t$-contrast (blue) that compares geometry related nouns to non-
        geometry related nouns spoken by the narrator
        (\texttt{geo, groom > all non-geo}) are overlaid over the movie's
        primary $t$-contrast (blue) that compares cuts to setting depicted for
        the first time with cuts within a recurring setting
        (\texttt{vse\_new > vpe\_old}).
        Black:
        outline of subject-specific PPA ROIs.
        Light gray: The
        audio-description's field of view (cf. \citep{hanke2014audiomovie}).
        To facilitate comparisons across subjects, we chose the same horizontal
        slice (x=-11) for all subjects as this slice depicts voxels of
        significant clusters in almost all subjects.
        The figure does not show voxels of the left cluster of the AV stimulus
        in sub-09 and sub-18, and voxels of the right cluster of the AV
        stimulus in sub-15.}
    \label{fig:subs-thresh-ppa}
\end{figure*}

% Bland-Altman-Plots
To better depict the agreement and difference between the results of the visual
localizer and the primary AD contrast, we created a Bland-Altman-Plot for every
subject (see Figure \ref{fig:bland-altman}).
% what it depicts
Each subplot visualizes the mean value and difference (localizer minus AD) of
two spatially corresponding voxels in the unthresholded $z$-maps.
% top KDE plot
A shift of the distribution to voxels with a mean above zero can be seen the
further we constrain voxels to the individual PPA (cf. KDE plot for the x-axes).
% right KDE plot
Values above the horizontal line depict voxels that show a higher $z$-value in
the dedicated localizer, values below the horizontal line depict voxels that
show a higher $z$-value in the AD stimulus.

>>>>

@@

% open question
In this study, we investigate if increased hemodynamic activity in the PPA that
is usually revealed by contrasting blocks of pictures can also be revealed under
more ecologically conditions.
% we use 2 naturalistic stimuli
To answer this question, we operationalized the perception of both visual and
auditory spatial information using two naturalistic stimuli (see
\citep{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic} for reviews).
% AV stimulus
The operationalization of visual perception is based on an annotation of cuts
and depicted locations in the audio-visual movie ``Forrest Gump''.
% AD stimulus
The operationalization of auditory perception is based on an annotation of
speech occurring in the movie's audio-description.
% GLM contrasts
We then created several general linear model (GLM) contrasts to analyze the
corresponding publicly available fMRI datasets of each naturalistic stimulus
\citep{hanke2016simultaneous, hanke2014audiomovie}
(\href{http://www.studyforrest.org}{studyforrest.org}).

@@

\subsection{Participants}
% AD study
In the audio-description study \citep{hanke2014audiomovie}, 20 German native speakers (all
right-handed, age 21–38 years, mean age 26.6 years, 12 male) listened to the
German audio-description \citep{ForrestGumpGermanAD} of the movie ``Forrest
Gump'' \citep{ForrestGumpMovie}.
% AV study
In the movie study \citep{hanke2016simultaneous}, 15 participants (21–39 years,
mean age 29.4, six female) of the prior audio-description study watched the audio-visual movie
with dubbed German audio track \citep{ForrestGumpDVD}.
% VIS study
In the VIS study \citep{sengupta2016extension}, the same 15 participants took
part in a six-category block-design visual localizer.

@@

% AD
In the audio-description study, visual instructions were presented on a rear-projection screen
inside scanner bore. During the
functional scans, the projector presented a medium gray screen with the primary
purpose to illuminate a participant's visual field in order to prevent premature
fatigue.
% AV & VIS
In the movie and VIS study, visual instructions and stimuli were presented on a
rear-projection screen
% screen size \unit[23.75 $\times$ 10.25]{cm}
at a viewing distance of \unit[63]{cm}, with a movie frame projection size
approximately \unit[21.3]$^{\circ}$ $\times$ \unit[9.3]$^{\circ}$.
% angle of view: VIS
In the VIS study, stimulus images were displayed at a size of approximately
\unit[10]$^{\circ}$ $\times$ \unit[10]$^{\circ}$ of visual angle.
% AD & AV: auditory stimulation
Auditory stimulation was implemented using custom in-ear (audio-description), or over-the-ear
headphones (movie), which reduced the scanner noise by
at least \unit[20–30]{dB}.

@@

Gradient-echo fMRI data for the audio-description study were acquired using a \unit[7]{Tesla}
Siemens MAGNETOM magnetic resonance scanner equipped with a 32 channel brain
receive coil at \unit[2]{s} repetition time (TR) with 36 axial slices (thickness
\unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane resolution, \unit[224]{mm}
field-of-view, anterior-to-posterior phase encoding direction) and a
\unit[10]{\%} inter-slice gap, recorded in ascending order.
% slice orientation
Slices were oriented to include the ventral portions of frontal and occipital
cortex while minimizing intersection with the eyeballs.
% FOV
The field of view was centered on the approximate location of Heschl's gyrus.
% motion correction
EPI images were online-corrected for motion and geometric distortions.

% AV & VIS
In the movie and VIS study, a \unit[3]{Tesla} Philips Achieva dStream
MRI scanner with a 32 channel head coil acquired gradient-echo fMRI data
at \unit[2]{s} repetition time with
% slices
35 axial slices (thickness \unit[3.0]{mm}, \unit[10]{\%} inter-slice gap) with
\unit[80 $\times$ 80]{voxels} (\unit[3.0 $\times$ 3.0]{mm} of in-plane
resolution, \unit[240]{mm} field-of-view) and an anterior-to-posterior phase
encoding direction, recorded in ascending order.
% no. of volumes
A total of 3599 volumes were recorded for each participant in each of the
naturalistic stimulus paradigms (audio-description and movie).

@@

% data sources
% https://github.com/psychoinformatics-de/studyforrest-data-aligned/tree/master/code
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}
All analyses presented here are based on previously published fMRI data
(\url{https://github.com/psychoinformatics-de/studyforrest-data-aligned}).
Of those 15 participants in the studyforrest dataset that took
part in all three experiments,
% exclusion of VP 10
data of one participant were dropped to due to invalid distortion correction
during scanning of the audio-description stimulus.
Data were previously corrected for motion, aligned with and re-sliced onto a
participant-specific BOLD template image \citep{sengupta2016extension}
(uniform spatial resolution of \unit[2.5$\times$2.5$\times$2.5]{mm} for both
audio-description and movie data).
% preprocessing intro
All analyses presented here were carried out using
FSL v5.0.9 (\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software Library};
\citep{smith2004fsl}) on a computer cluster running the Debian GNU/Linux
operating system. Software packages were obtained from repositories of
\href{http://neuro.debian.net}{NeuroDebian} \citep{halchenko2012open}.

@@

% AV anno
For the analysis of the movie stimulus, we took advantage of a previously published
annotation of 869 movie cuts and the depicted location after each cut
\citep{haeusler2016cutanno}.
% rationale to use that annotation rationale behind using movie cuts
Our rationale was that cuts are ``spatially relevant'' events that re-orient the
viewer within the environment of the movie by either switching to another
setting or switching the perspective within the same setting.
% AV regressors/events
Each cut was put into one of the following five categories (see Table
\ref{tab:av-events}):
%
1) a cut switching to a setting that was depicted for the first time
(\texttt{vse\_new}),
%
2) a cut switching to a setting that was already depicted earlier in the movie
(\texttt{vse\_old}),
%
3) a cut switching to another locale within a setting (\texttt{vlo\_ch}; e.g. a
cut from first to the second floor in Forrest's house),
%
4) a cut to another camera position within a setting or locale that was depicted
for the first time (\texttt{vpe\_new}), and
%
5) a cut to another camera position within a setting or locale that was already
depicted before (\texttt{vpe\_old}).

@@

% AD annotation
For the analysis of the audio-description stimulus, we extended a publicly available annotation
of speech \citep{hausler2021studyforrest} by further annotating words spoken by
the audio-description's narrator.
% annotation procedure
Two persons performed a categorization of (concrete and countable) nouns that
the narrator uses to describe the movie's missing visual content based on a set
of rules.
% preliminary annotation
A preliminary annotation was performed by one person according to the rules.
% corrections
Minor corrections due to incorrectly applied rules were done by the author.
% reference to table with rules and examples
A complete overview of all 18 noun categories, the rule for a word to belong to
a category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% why and how of categories 1
Some categories reflect the verbal counterpart of the stimulus categories that
were used in the visual localizer experiment (e.g. \texttt{body}, \texttt{face},
\texttt{head}, \texttt{object}, \texttt{setting\_new}, and
\texttt{setting\_rec}).
% why and how of categories 2
Other categories were created to semantically cluster remaining nouns into
categories that had no counterpart in the visual localizer experiment (e.g.
\texttt{bodypart}, \texttt{female}, \texttt{fname}, \texttt{furniture},
\texttt{geo}, \texttt{geo-room}, \texttt{male}, and \texttt{persons}).
% categories in detail
%Nouns were categorized by the verbal clue they provide about the
%cinematographic scene's environment (\texttt{geo}, \texttt{geo-room};
%\texttt{setting\_new}, \texttt{setting\_old}), its inherent persons (e.g.
%\texttt{female}, \texttt{male}, \texttt{persons}), a person's body or worn
%clothes (\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a
%scene's inherent objects (\texttt{object}, \texttt{furniture}).  problem with
%hierarchical categories
The categories \texttt{setting\_new} and \texttt{setting\_rec} comprise not just
words that describe a setting as a whole (e.g. ``[in] Greenbow'', ``[in a]
disco'', ``[the platoon wades through a] rice field''). They also comprise words
that could count as a member of another category in case the narrator uses
these words to indicate a switch from one setting to another (e.g. ``[a]
physician'').
% how it was handled
These nouns were flagged with both categories during the initial annotation
procedure. In context of the current analyses these word are considered to
belong exclusively to the higher-level category of changing a setting
(\texttt{se\_new} or \texttt{se\_old}).
% pooling of categories
Some noun categories that were semantically similar and offered only a small
amount of counts were pooled resulting in 11 final event categories (see Table
\ref{tab:ao-events}). These event categories were then used to model hemodynamic
responses.

@@

% low-leve confounds: intro
Lastly, we algorithmically annotated the temporal structure of low-level
perceptual features to create nuisance regressors.
% visual shit
For the movie stimulus, we computed the mean luminance of a movie frame
(\unit[40]{ms}), the difference in mean luminance of each frame's left and right
half, the difference in mean luminance of the lower and upper half, and finally
the perceptual difference of consecutive frames.
% auditory shit
Finally for both audio tracks, we computed the left-right difference in volume
and root mean square energy averaged across the length of every movie frame
(\unit[40]{ms}).

@@

% movie events
The events of the movie cut related categories and \texttt{no\_cut} events were
modeled as box car events of 200 ms duration.
%
Nouns were modeled from onset to offset of each word, low-level confounds from
onset to offset of the corresponding movie frame
% convolving
Events for all regressors of the movie and audio-description stimulus were convolved with a double
gamma hemodynamic response function (HRF).

@@

% AV design matrix
For the subsequent first level GLM analysis of the movie stimulus, the modeled
hemodynamic responses related to all movie cuts (including \texttt{no\_cut}) and
six low-level perceptual confounds were included as regressors in the design
matrix.
% AD regressors in AV AD design matrix
For the first level analysis of the audio-description stimulus, the modeled hemodynamic
responses related to all noun categories and the two low-level perceptual
confounds were included.
% AD regressors in AV
To create a contrasts of cross-modal control in the analysis of the movie stimulus,
we also implemented the regressors based on nouns used by the
audio-description's narrator to indicate a switch to another setting (categories
\texttt{se\_new} and \texttt{se\_old}).
% AV regressors in AV
To create contrasts of cross-modal negative control in the analysis of the audio-description
stimulus, we also implemented the movie cut-related regressors
(excluding \texttt{no\_cut}).
% both stimuli: null regressors
For both stimuli, a null regressor was chosen for a event category in a segment,
if that segment did not contain an event of the category (e.g. no event of
\texttt{vpe\_old} in segment 3; cf. Table \ref{tab:ao-events}).
% temporal derivatives
Temporal derivatives were included in the design matrix to compensate for
regional differences between modeled and actual HRF \citep{friston1998event}.
% motion parameters
Six motion parameters were also included.
% high-pass filtering
Finally, designs were filtered with the same high-pass filter (cutoff period of
\unit[150]{s}) as the BOLD time series.

@@

% similar to previous studies
On the first level, we created GLM contrasts based on annotated stimulus
features embedded in the in the audio-visual movie and its audio-description.
% intro
To test the robustness of this approach, we operationalized the perception of
spatial information compared to the perception of non-spatial information
differently in five $t$-contrasts for the movie stimulus (see Table
\ref{tab:av-contrasts}) and eight $t$-contrasts for the audio-description stimulus (see Table
\ref{tab:ao-contrasts}).
% reason: robustness
We assumed all contrasts could in principle correlate with increased hemodynamic
activity in the PPA but chose one contrast to be the ``primary contrast'' for
later detailed inspection and report.
% selection criteria for primary contrast.
The selection criterion for the primary contrast of each stimulus was a
subjectively good balance between a) how well the average of events within
categories represented spatial information and non-spatial information
respectively (cf. section \ref{rationale}), and b) the amount of available data.
% AV: primary contrast
In the primary contrast of the movie stimulus, we contrasted cuts to a setting that
was not depicted before (\texttt{vse\_new}) to cuts merely switching the camera
position within a setting that was already established earlier in the movie
(\texttt{vpe\_old}).
% why
We assumed that the category \texttt{vse\_new} on average comprised the most
movie frames depicting a landscape or the geometry of a setting, and the
category \texttt{vpe\_old} the most frames depicting persons, faces, or objects
[(cf.  rationale to categorize the cuts in section \ref{rationale})].
% AD: primary contrast
In the primary contrast of the audio-description stimulus, we contrasted buildings and
landmarks (\texttt{geo}), and rooms and geometry-defining objects
(\texttt{geo-room}) with not just nouns referring to a person's head or face
(\texttt{fahead}, N=83; e.g.  ``eyes'', ``face'', or ``head'') but also all
non-geometry related categories (\texttt{body}, \texttt{bodypart},
\texttt{fahead}, \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}) except
\texttt{furniture} to get more events per stimulus segment.\todo{ouff}
% why furniture was not used
The category ``furniture'' (\texttt{furn}) was not used as a regressor of
interest in any contrast because these nouns could be perceived as either a
geometry-defining scene element or as an isolated object.
% why se_new & se_old were not used in the primary contrasts
The categories of nouns indicating a switch to a setting that occurred for the
first time (\texttt{se\_new}) or a setting that recurred during the plot
(\texttt{se\_old}) were not included in the primary contrast because
% heterogeneous category
a) categories comprise nouns that could count as a member of another category
(e.g. ``[a] physician''; section \ref{rationale}), and
% richness of verbal description vs. picture
b) nouns that only vaguely describe a scene (e.g. ``[in] Greenbow'', ``[in a]
disco'', ''[black and white] film recordings'') [compared to whole, perceptually
richer pictures].
% and c) the narrator is often lacking behind a short dialogue or a change of
% the soundscape that might already indicate a change of settings.

% control contrasts
Finally, we created several $t$-contrasts as negative controls for both stimuli
(see Tables \ref{tab:av-contrasts} and \ref{tab:ao-contrasts}).
% AV: no cut > cut
For the movie stimulus, four contrasts were created contrasting the no-cut
regressor (\texttt{vno\_cut} to cut-related regressors \ref{tab:av-contrasts}).
% AV: narrator
One contrast (\texttt{vs\_new} > \texttt{vpe\_old}) was created by contrasting
nouns spoken by the narrator.
% AD stimulus
For the audio-description stimulus, we created five $t$-contrasts (see Table
\ref{tab:ao-contrasts}) to test if increased activation in the PPA was
correlated with moments of cuts.

@@

% one contrast to localize them all; "...and Z>3.4 for all"
Contrary to \citep{sengupta2016extension}, we here used the same contrast of
each naturalistic stimulus and the same threshold for all subjects.
% subject space -> NeuroVault
Results of the analyses that were performed in subject-space can be found in the
accompanying dataset (Z>2.3, p<.05 cluster-corrected).
% here report in group space
For better comparisons of subjects, we here report results from the analyses
performed in group space (Z>3.4, p<.05 cluster-corrected).
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary movie
and audio-description $t$-contrast, and the outline of overlapped, individual PPAs
co-registered to the MNI152 template.
% one slice to show them all
Transversal slice of z=-11 was chosen as it depicts voxels of
significant clusters in almost all subjects.

% AV
Results of the primary movie contrast yielded bilateral clusters in five subjects,
a unilateral right cluster in six subjects (of which one subjects yielded a
unilateral cluster in the visual localizer), and a unilateral left cluster in
one subject.
% difference to dedicated localizer
We find homologous clusters in sub-20, whereas the dedicated visual localizer
yielded only one cluster in the right hemisphere.

% report here in group
Results of the primary audio-description contrast yielded bilateral clusters in nine subjects
that are within or overlapping with the individual PPA.
% subj-04
In sub-04, two homologous clusters are apparent, whereas the dedicated localizer
(and movie stimulus) yielded only one cluster in the right hemisphere.
% sub-09
In sub-09 the analysis yielded one cluster in the left-hemispheric PPA.

\begin{figure*}[h!]
\centering
    \includegraphics[width=\linewidth]{figures/subs-thresh-ppa}
    \caption{Fixed-effects individual-level GLM results (Z>3.4, p<.05
        cluster-corrected).
        Individual brains are aligned via non-linear
        transformation to a study-specific T2* group template that is
        co-registered to the MNI152 template with an affine transformation (12
        degrees of freedom).
        The results of the audio-description's primary
        $t$-contrast (blue) that compares geometry related nouns to non-
        geometry related nouns spoken by the narrator
        (\texttt{geo, groom > all non-geo}) are overlaid over the movie's
        primary $t$-contrast (blue) that compares cuts to setting depicted for
        the first time with cuts within a recurring setting
        (\texttt{vse\_new > vpe\_old}).
        Black:
        outline of subject-specific PPA ROIs.
        Light gray: The
        audio-description's field of view (cf. \citep{hanke2014audiomovie}).
        To facilitate comparisons across subjects, we chose the same horizontal
        slice (x=-11) for all subjects as this slice depicts voxels of
        significant clusters in almost all subjects.
        The figure does not show voxels of the left cluster of the movie stimulus
        in sub-09 and sub-18, and voxels of the right cluster of the movie
        stimulus in sub-15.}
    \label{fig:subs-thresh-ppa}
\end{figure*}

% Bland-Altman-Plots
To better depict the agreement and difference between the results of the visual
localizer and the primary audio-description contrast, we created a Bland-Altman-Plot for every
subject (see Figure \ref{fig:bland-altman}).
% what it depicts
Each subplot visualizes the mean value and difference (localizer minus audio-description) of
two spatially corresponding voxels in the unthresholded $z$-maps.
% top KDE plot
A shift of the distribution to voxels with a mean above zero can be seen the
further we constrain voxels to the individual PPA (cf. KDE plot for the x-axes).
% right KDE plot
Values above the horizontal line depict voxels that show a higher $z$-value in
the dedicated localizer, values below the horizontal line depict voxels that
show a higher $z$-value in the audio-description stimulus.
